Stellar Migration and Chemical Enrichment in the Milky Way Disk: Predictions of a Hybrid Model

### 2021-08-04 chemev/MWbimodality/paper/outline3/outline3.tex
migration paper referee response

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\providecommand{\noopsort}[1]{} 
\graphicspath{ {../plots/} }

@@

\title{Stellar Migration and Chemical Enrichment in the Milky Way}

@@

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
simulation of galaxy evolution. We find that models for the 
time-dependence of radial migration impact the type Ia supernova rate as a 
function of both time and radius, inducing significant variability. We 
demonstrate that this is a means with which young, $\alpha$-enhanced stars can 
arise naturally out of inside-out galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[O/H] and age-[Fe/H] relations are well-fit by 
a late starburst model; no one model investigated here fits both 
simultaneously. We also find that our models predict a dichotomy in 
[$\alpha$/Fe], but that they do not resemble that observed in the Milky Way 
due to an overabundance of intermediate [$\alpha$/Fe] stars. This suggests 
that inside-out galaxy growth combined with radial migration, even with a late 
starburst, is not conducive to forming the infamous bimodality as it is 
observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
two-infall model) may be necessary to describe the observed results. In 
conducting this analysis, we developed and made use of newly released features 
in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
which are built to handle these simulations under a wide variety of 
assumptions. \texttt{VICE} is publicly available 
at~\url{https://pypi.org/project/vice}. 
\end{abstract}

@@

\section{Introduction} 
\label{sec:intro} 
\begin{itemize} 
	\item Known for some time that stars undergo radial migration 
	\citep[e.g.][]{Wielen1996}, but to date there are only a handful of 
	chemical evolution models that take this into account 
	\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}. This effect can 
	have a considerable impact on observed abundance trends by mixing stars 
	that formed out of Galactic regions with significantly different 
	enrichment histories, and if not taken into account, will impact the 
	conclusions of chemical evolution studies.

		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
		are statistically older than solar metallicity stars (their Fig. 3). 
		Contrasts with simple one-zone models where enrichment proceeds 
		alongside star formation yielding a monotonic 
		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
		starbursts can produce non-monotonic AMR due to the effect of 
		dilution~\citep{Johnson2020}, but they by construction do not predict 
		multiple abundances at fixed age. Argued using 
		the~\citet{Weinberg2017} 
		% the~\mniiiauthor{Weinberg}{Andrews}{Freudenburg}  
		analytic models that this is a consequence of radial migration - for a 
		smooth star formation history (SFH), the youngest stars at any given 
		radius will have composition reflective of the local equilibrium 
		abundance, and only older stars will have had adequate time to 
		migrate to a similar Galactocentric radius. 
	\end{itemize}

		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
		models to observed stellar luminosity functions and color-magnitude 
		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
		similar conclusions by modeling the white dwarf luminosity function in 
		the solar neighbourhood with Gaia parallaxes. Motivated by these 
		results, \citet{Johnson2020} demonstrate using one-zone chemical 
		evolution models that a recent starburst can produce young, 
		$\alpha$-enhanced stars. Caveat: burst would have had to be 
		sufficiently localized such that the young,~$\alpha$-rich stars remain 
		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
		relation. 
	\end{itemize}

@@

		\item \citet{Spitoni2019} demonstrate that two-infall models can 
		reproduce solar annulus data with good agreement. This plus 
		radial migration is yet unexplored.

@@

	\item This paper is meant to address the following simple question: When 
	combining simple, conventional assumptions about the star formation and 
	dynamical histories of the Milky Way, what observed results can be 
	replicated? 
\end{itemize}

@@

\begin{itemize} 
	\item To address the main goal of this paper, we make use of multi-zone 
	chemical evolution models in which the Milky Way is described by a series 
	of concentric annuli. Examples of similar methodologies already in 
	the literature can be found in~\citet{Matteucci1989}, 
	\citet{Schoenrich2009},~\citet{Minchev2013}, and~\citet{Sharma2020}. Here 
	we entertain a handful of models describing the star formation history and 
	the time-dependence of radial migration, then simply assess their 
	predictions in comparison to the results discussed in~\S~\ref{sec:intro}.

	\item Multizone models are a means of extending traditional one-zone 
	models to take into account the motions of stars and gas by allowing the 
	exchange of both between zones.

	\item Our fiducial model has an inside-out star formation history (SFH) 
	with parameters motivated by various observational constraints. Motivated 
	by the findings of~\citet{Mor2019} and~\citet{Isern2019}, we construct a 
	model with a late burst of star formation for comparison. A starburst of 
	similar form was investigated in one-zone models in~\citet{Johnson2020}. 
	For comparison, we also construct a model in which the SFH is constant 
	with time at fixed Galactocentric radius. This is interesting primarily 
	from a theoretical perspective; it removes the effects of a time-varying 
	SFH and quantifies what is predicted when there is ongoing star formation 
	with radial migration.

	\item To include the effects of 
	stellar migration, we make use of data from a hydrodynamical simulation, 
	discussed in~\S~\ref{sec:methods:h277}. This allows us to adopt the 
	dynamical history of a much more sophisticated simulation at face value, 
	providing us with a model for radial migration that requires no free 
	parameters. 
	\begin{itemize} 
		\item The~\citet{Schoenrich2009},~\citet{Minchev2013}, and 
		\citet{Sharma2020} studies chose a model for radial migration that 
		was based on dynamical arguments, which introduced free parameters 
		that then required fitting to data. An advantage of our decision to 
		make use of a hydrodynamical simulation over dynamical arguments is 
		that it's unclear the extent to which fitting to observed data biases 
		the model into agreement with parts of the data that weren't involved 
		in the fit. A hydrodynamical simulation, while still an approximation 
		of reality, is motivated by first principles in that it models the 
		gravitational interactions of star particles with gas and other star 
		particles as well as the diffuse dark matter halo. Furthermore, we 
		choose here a hydrodynamical simulation which is ran from cosmological 
		initial conditions.

		\item The primary disadvantage of this choice is a consequence of the 
		lack of free parameters - the model is rigid, and we cannot explore 
		slight variations. However, in principle one could compare the 
		predictions made by the same chemical evolution models but with 
		different hydrodynamical simulations. 
	\end{itemize}

	\item To fulfill the goals of this paper, we develop and make use of 
	newly released features within the~\texttt{Versatile Integrator for 
	Chemical Evolution} (\texttt{VICE}), which are designed to handle these 
	kinds of simulation with a wide range of flexibility. We reserve 
	description of~\texttt{VICE}'s algorithm for~\S 
	\ref{sec:methods:migration}, first describing our sample of star 
	particles from the hydrodynamical simulation. 
\end{itemize}

@@

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our candidate analog star particles 
from~\texttt{h277}. In the top row, we show distributions of~\textit{final} 
radius in bins of birth radius and age. In the bottom row, we show 
distributions of~\textit{birth} radius in bins of final radius and age. Each 
bin in Galactocentric radius is shown in its own panel, denoted in text at the 
top of each panel and by vertical black dashed lines. We color-code the 
distributions according to the age of the star particles, denoted by the 
legend in the upper left panel. We smooth all distributions with a box-car 
width of 0.5 kpc to improve clarity. We omit the distributions for 8 - 10 Gyr 
old stars born in the 9 - 11 and 11 - 13 kpc bins due to an insufficient 
number of star particles with which to calculate the distribution. }
\label{fig:h277_decomposition} 
\end{figure*}

@@

	\item We find that only~$\sim$3\% of~\texttt{h277}'s star particles formed 
	within the first 1 Gyr of its 13.7 Gyr run, indicating that $T$ = 1 Gyr 
	is a much better estimate of the onset of star formation and thus the 
	chemical evolution in~\texttt{h277} than $T$ = 0. We thus remove the star 
	particles that were born in the first Gyr of evolution, and subtract 1 Gyr 
	from their formation times, thus running our disc models for 12.7 Gyr. As 
	a result, our simulations run from a redshift of~$z \approx$ 3 to the 
	present day.

@@

	\item Based on a kinematic decomposition performed on the present-day 
	phase space distribution of the~\texttt{h277} star particles, we exclude 
	halo stars, but include bulge, pseudobulge, and thin- and thick-disc 
	stars. Even though we are not modeling the abundances in the bulge in this 
	paper, the bulge is believed to have formed in-situ ({\color{red} 
	citation}), while a significant fraction of halo stars are believed to 
	have been accreted ({\color{red} citation}). It's also likely that the 
	Milky Way bulge and disc exchanged statistically significant amounts of 
	stars and gas ({\color{red} citation}), coupling the chemical evolution of 
	the two at least slightly. This effect can be addressed in our models by 
	simply including these star particles in our sample. This yields a sample 
	of 3,019,521 star particles from~\texttt{h277}.

	\item \texttt{h277} had a transient bar during its evolution, but does 
	not have a bar at $z$ = 0. This could mean that the star particles 
	in~\texttt{h277} migrated in a manner which does not reflect the dynamical 
	history of the Milky Way, but at present inferring a star's birth radius 
	observationally is notoriously difficult anyway ({\color{red} citation}), 
	so its likely the impact of this decision is within current 
	observational uncertainties. Nonetheless, it is worth noting that 
	the~\citet{Minchev2013} model, and by extension the~\citet{Minchev2014} 
	and~\citet{Minchev2017} studies as well, selected a hydrodynamical 
	simulation specifically so that it would have a bar at $z$ = 0. A detailed 
	investigation of the impact of bar evolution on stellar migration and thus 
	chemical evolution is outside the scope of this paper, though can be 
	conducted in principle by simply swapping the birth times and initial and 
	final radii of~\texttt{h277} within~\texttt{VICE}, rerunning the 
	simulations, and comparing the results.

@@

\subsection{Radial Migration} 
\label{sec:methods:migration} 
\begin{itemize} 
	\item To simulate our models, we develop and make use of \texttt{VICE}'s 
	\texttt{milkyway} object, an extension of a more general object named 
	\texttt{multizone}. The \texttt{multizone} object is at its core an array 
	of \texttt{singlezone} objects, which are designed to handle 
	simulations of one-zone models and were the focus of 
	\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
	\texttt{multizone} object then affords the user the ability to move 
	gas between zones with any given time dependence, and to assign all 
	stellar populations any given zone at any given time following their 
	birth, effectively allowing arbitrarily complex zone and migration 
	schema. The \texttt{milkyway} object is a user-friendly extension of this 
	which enforces a zone configuration in which the Galaxy is modeled as a 
	series of concentric annuli of uniform width~$\Delta R_\text{gal}$. As 
	defaults, it adopts the stellar migration model described in this section 
	{\color{red}and our star formation law described in~\S 
	\ref{sec:methods:sfe}.}

@@

	\item In modeling the Milky Way as a series of concentric annuli,
	~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations to 
	be born at the centres of each annulus. 
	For a stellar population born at time $T$ and Galactocentric radius 
	$R_\text{gal}$, it searches for star particles from~\texttt{h277} that formed at $T \pm$ 300 Myr and $R_\text{gal} \pm$ 250 pc. It then randomly 
	selects a star particle from this subsample with no bias to act as 
	an~\textit{analog}. Adopts the final radius of the analog star particle at 
	face value, and moves from its radius of birth to the final radius at $T$ 
	= 12.7 Gyr with some time dependence. If no candidate analogs are found, 
	search is widened to $T \pm$ 600 Myr and $R_\text{gal} \pm$ 500 pc. If 
	still no candidate analogs are found in this widened search, the stellar 
	population is assumed to remain at its birth radius {\color{red} and to 
	have a final height above the disc midplane of $z$ = 100 kpc.} These 
	stellar populations are few in number. In our fiducial model with an 
	inside-out SFH (see~\S~\ref{sec:methods:sfhs}), these stellar populations 
	account for~$\sim$4.9\% of the simulated stellar populations by number, 
	but only~$\sim$0.56\% by mass. Making up such a small portion of the mass 
	budget, it's not likely they contribute significantly to the chemical 
	evolution of our model Galaxy. 
	\begin{itemize} 
		\item We have zones for each annulus from $R_\text{gal}$ = 0 to 
		20 kpc; there are no zones off the midplane. This retains the 
		assumption that the gas-phase abundances are vertically and 
		azimuthally well-mixed. Each stellar population simply assumes the 
		final height~$\left|z\right|$ above the disc midplane of its assigned 
		analog, though this doesn't enter into the simulations at all; it's 
		purely post-processing information. 
	\end{itemize}

	\item When a star particle is assigned as an analog to a stellar 
	population in our simulations, it is~\textit{not} thrown out of the sample 
	of candidate analogs, in theory allowing a star particle to act as an 
	analog for multiple stellar populations. This is a difference between 
	the~\citet{Minchev2013} model and ours. Where we assign star particles to 
	stellar populations for which~\texttt{VICE} then calculates a stellar mass 
	and composition based on an assumed star formation history, the 
	\citet{Minchev2013} model assigns compositions to star particles.

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time 
for two stellar populations under our migration schema: diffusion (crimson, 
solid), linear (lime, dot-dashed), post-process (black, dotted), and 
sudden (blue, dashed). Here the initial and final radii and birth times are 
chosen at random for illustrative purposes. With the initial and final 
Galactocentric radii of a stellar population, its birth time, and one of these 
assumptions about the time-dependence of migration, the Galactocentric radius 
at all times is known. } 
\label{fig:migration_schema} 
\end{figure}

	\item Our migration models 
	\begin{itemize} 
		\item All neglect radial gas flows, this paper instead focusing on 
		four simple models for how the radius of a stellar population's orbit 
		changes with time. Investigation of our models with radial gas flows 
		would be an interesting extension to this paper.

@@

		\item \textbf{Diffusion}: A case in which stars migrate in a 
		continuous, time-dependent manner. If stars move to their final 
		radii via a random walk, then the mean displacement of stars that 
		migrate similar distances would scale with~$\sqrt{\text{age}}$. This 
		is shown in the red solid line in Fig.~\ref{fig:migration_schema}. 
		This is our fiducial migration model; we present results using this 
		model except where otherwise noted. It is so named because it 
		corresponds to a scenario in which the random walk carries out the 
		diffusion of angular momentum.

@@

	\item We have a sample of 3,019,521 candidate analog star particles 
	from~\texttt{h277}, only~$\sim$57\% of which are disc stars. Since we're 
	modeling the thin and thick disc populations here,~$\sim$1.72 million is a 
	much better estimate of the number of analogs that we can realistically 
	sample from. We let star formation extend out to 15.5 kpc, beyond which 
	we force the star formation rate to zero at all times.~\texttt{VICE} does 
	form stellar populations at all timesteps in the annuli; they simply have 
	zero mass and thus do not contribute to the chemical evolution or 
	recycling, though they do contribute to the computational overhead. We 
	take $\Delta R_\text{gal}$ = 100 pc as the width of each annulus from 
	$R_\text{gal}$ = 0 to 20 kpc and a timestep size of $\Delta T$ = 10 Myr 
	from $T$ = 0 to 12.7 Gyr (see discussion in~\S~\ref{sec:methods:h277} for 
	our choice of time-interval). With the resulting 200 zones and 1,271 
	timesteps, we let~\texttt{VICE} form~$n$ = 8 stellar 
	populations per zone per timestep, resulting in 2,033,600 stellar 
	populations with predicted masses and abundances, 1,574,800 of which form 
	between~$R_\text{gal}$ = 0 and 15.5 kpc and have nonzero mass, reasonably 
	within the limit of what we can sample. These simulations run in~$\sim$2 
	hours and take up~$\sim$235 MB of disc space per output, including the 
	extra data that we record for each stellar population's analog star 
	particle. 
\end{itemize}

>>>>

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
\providecommand{\noopsort}[1]{} 
\graphicspath{ {../plots/} }

@@

\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
Chemical Enrichment in the Milky Way Disk: Predictions of a Hybrid Model}

@@

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
simulation of galaxy evolution. We find that models for the 
time-dependence of radial migration impact the type Ia supernova rate as a 
function of both time and radius, inducing significant variability. We 
demonstrate that this is a means with which young, $\alpha$-enhanced stars can 
arise naturally out of inside-out galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[O/H] and age-[Fe/H] relations are well-fit by 
a late starburst model; no one model investigated here fits both 
simultaneously. Our model successfully reproduces the broad nature of the 
[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
it from explaining the observed results in detail. This suggests 
that inside-out galaxy growth combined with radial migration, even with a late 
starburst, is not conducive to forming the infamous bimodality as it is 
observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
two-infall model) may be necessary to describe the observed results. In 
conducting this analysis, we developed and made use of newly released features 
in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
which are built to handle these simulations under a wide variety of 
assumptions. \texttt{VICE} is publicly available 
at~\url{https://pypi.org/project/vice}. 
\end{abstract}

@@

\section{Introduction} 
\label{sec:intro} 
\begin{itemize} 
	\item Known for some time that stars undergo radial migration 
	\citep[e.g.][]{Wielen1996}; this is an effect which could considerably 
	impact chemical evolution in galaxies by mixing stars that formed in 
	different galactic regions with significantly different enrichment 
	histories.

	\item To date there are only a handful of models which attempt to include 
	this information, all focused on the Milky Way~\citep[e.g.][]{Matteucci1989, 
	Schoenrich2009, Minchev2013, Sharma2020}. Each of these 
	studies treated the Milky Way as a series of concentric annuli, each 
	described by a conventional one-zone model with parameters that change from 
	annulus to annulus. In the resultant ``multi-zone'' model, stars and gas 
	migrate between zones under some prescription to account for mixing 
	processes. In this paper, we adopt an approach similar to that used by 
	\citet{Minchev2013}, in which the mixing processes are informed by star 
	particles from a hydrodynamical simulation ran from cosmological initial 
	conditions. With parameters tuned to reproduce observed results, such as 
	abundance and surface density gradients, we can then assess the model 
	predictions to address the following question: when combining simple, 
	conventional assumptions about the star formation and dynamical histories 
	of the Milky Way, what observed results can be replicated?

	\item The observables that we focus on are: 
	\begin{itemize} 
		\item Metallicity distributions and abundance gradients

		\item The [$\alpha$/Fe] bimodality

		\item The age-metallicty relation (AMR)

		\item The young, $\alpha$-rich population
	\end{itemize}

@@

		\item \citet{Spitoni2019, Spitoni2020} demonstrate that two-infall 
		models can reproduce solar annulus data with good agreement. Recently, 
		\citet{Spitoni2021} argued that this extends to other regions of the 
		Galactic disc by reproducing APOGEE DR16 abundances by means of a 
		chemical evolution model with three annuli centered on 4, 8, and 12 
		kpc. Although they're able to reproduce the data for different regions 
		of the Galaxy, their model does not include a treatment for the 
		migration of stars beyond their birth radius; though with 4-kpc annuli, 
		it's not likely there would be much impact given the coarse nature of 
		the binning.

@@

		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
		are statistically older than solar metallicity stars (their Fig. 3). 
		Contrasts with simple one-zone models where enrichment proceeds 
		alongside star formation yielding a monotonic 
		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
		starbursts can produce non-monotonic AMR due to the effect of 
		dilution~\citep{Johnson2020}, but they by construction do not predict 
		multiple abundances at fixed age. Argued using 
		the~\citet{Weinberg2017} 
		analytic models that this is a consequence of radial migration - for a 
		smooth star formation history (SFH), the youngest stars at any given 
		radius will have composition reflective of the local equilibrium 
		abundance, and only older stars will have had adequate time to 
		migrate to a similar Galactocentric radius. 
	\end{itemize}

		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
		models to observed stellar luminosity functions and color-magnitude 
		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
		similar conclusions by modeling the white dwarf luminosity function in 
		the solar neighbourhood with Gaia parallaxes. Motivated by these 
		results, \citet{Johnson2020} demonstrate using one-zone chemical 
		evolution models that a recent starburst can produce young, 
		$\alpha$-enhanced stars. Caveat: burst would have had to be 
		sufficiently localized such that the young,~$\alpha$-rich stars remain 
		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
		relation. 
		\begin{itemize} 
			\item The impact of such evolutionary histories combined with a 
			model for stellar migration is, to our knowledge, yet unexplored in 
			the literature. 
		\end{itemize} 
	\end{itemize}

	\item A viable model for the detailed enrichment history of the Milky Way 
	would explain simultaneously all of these observed results and their 
	variations in different Galactic regions, while also taking into account 
	effects like mixing and observational systematics. In this paper, we aim to 
	assess the extent to which conventional assumptions about the evolutionary 
	history of the Milky Way can account for these results, entertaining a 
	handful of models describing the star formation history and time-dependence 
	of radial migration. 
	\begin{itemize} 
		\item Motivated by the general result that Galaxies grow in radius 
		(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model 
		has a star formation history whose e-folding timescales grow with 
		Galactocentric radius. Motivated by the findings of~\citet{Mor2019} 
		and~\citet{Isern2019}, we also construct models which exhibit a recent 
		enhancement in the star formation rate. For comparison, we also 
		construct a model in which the SFH is constant with time at fixed 
		radius; this is interesting primarily from a theoretical perspective, 
		removing the effects of a time-varying SFH to quantify only what is 
		predicted by ongoing star formation with radial mixing.

		\item While we make use of a hydrodynamical simulation to include the 
		effects of radial migration, we do~\textit{not} make use of its star 
		formation history. While~\citet{Minchev2013} also made use of a 
		hydrodynamical simulation in their study, ours differs from theirs in 
		this key aspect. The~\citet{Schoenrich2009} and~\citet{Sharma2020} 
		studies, on the other hand, chose a model for radial migration that was 
		based on dynamical arguments, which introduced free parameters that 
		then required fitting to data. An advantage of our decision to make use 
		of a hydrodynamical simulation over dynamical arguments is that it's 
		unclear the extent to which fitting to observed data biases the model 
		into agreement with parts of the data that weren't part of the fit. A 
		hydrodynamical simulation, while still an approximation of reality, 
		is motivated by first principles in that it models the gravitational 
		interactions of star particles with gas and other star particles as 
		well as the diffuse dark matter halo. The primary disadvantage of this 
		choice is a consequence of the lack of free parameters - the model is 
		rigid, and we cannot explore slight variations. However, in principle 
		one could compare the predictions made by our chemical evolution models 
		but with different hydrodynamical simulations. 
	\end{itemize}

@@

\begin{itemize} 
	\item To fulfill the goals of this paper, we develop and make use of 
	newly released features within the~\texttt{Versatile Integrator for 
	Chemical Evolution} (\texttt{VICE}), which are designed to handle these 
	kinds of simulation with a wide range of flexibility. We reserve 
	description of~\texttt{VICE}'s algorithm and our simulation parameters 
	for~\S~\ref{sec:methods:migration}, first describing our sample of star 
	particles from the hydrodynamical simulation.

	\item We emphasize that the star particles from the hydrodynamical 
	simulation are used~\textit{only} in the mixing component of our models. 
	We make use of neither its star formation nor chemical enrichment 
	histories; rather, these are exactly what we explore variations of in this 
	paper. There is no N-body integration involved in our models. 
\end{itemize}

@@

% fig 1 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our candidate analog star particles 
from~\texttt{h277}. In the top row, we show distributions of~\textit{final} 
radius in bins of birth radius and age. In the bottom row, we show 
distributions of~\textit{birth} radius in bins of final radius and age. Each 
bin in Galactocentric radius is shown in its own panel, denoted in text at the 
top of each panel and by vertical black dashed lines. We color-code the 
distributions according to the age of the star particles, denoted by the 
legend in the upper left panel. We smooth all distributions with a box-car 
width of 0.5 kpc to improve clarity. We omit the distributions for 8 - 10 Gyr 
old stars born in the 9 - 11 and 11 - 13 kpc bins due to an insufficient 
number of star particles with which to calculate the distribution. }
\label{fig:h277_decomposition} 
\end{figure*}

@@

@@

	\item Of the star particles with ages at first snapshot of~$\leq$~150 Myr, 
	the oldest star is 12.26 Gyr old at the present day. Since~\texttt{h277} 
	ran for 13.7 Gyr, we therefore subtract 1.5 Gyr from the formation times of 
	all star particles, and run our disc models for 12.2 Gyr. This value of 
	$T$ = 1.5 Gyr is likely tied to the onset of star formation in the 
	\texttt{h277} disc, which would have occurred some time following the 
	cosmological initial conditions at a lookback time of 13.7 Gyr. As a result, 
	our disc models trace the chemical evolution of the Milky Way out to a 
	lookback time of 12.2 Gyr, or a redshift of~$z \approx$ 3.

	\item We further restrict the sample of star particles to only those with 
	both formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have 
	formed within~$\left|z\right|\leq$~3 kpc of the disc midplane. These 
	criteria ensure that we're only using star particles which formed in-situ. 
	While it's possible that some star particles formed in a dwarf galaxy as it 
	was infalling which would satisfy these criteria, these star particles 
	are small in number, and are only relevant at large $R_\text{gal}$ and high 
	ages, a region of parameter space where few stars form anyway.

	\item Based on a kinematic decomposition performed on the present-day 
	phase space distribution of the~\texttt{h277} star particles, we include 
	all stars with bulge, pseudobulge, and disc-like kinematics, excluding the 
	halo stars. While we're not modeling the evolution of the bulge here, these 
	star particles are overwhelmingly located at~$R_\text{gal} \leq$~3 kpc at 
	the present day anyway, while we're interested in~$R_\text{gal} \geq$~3 kpc 
	in this paper since we're modeling the disc. This yields a sample of 
	3,000,556 star particles from~\texttt{h277}.

	\item \texttt{h277} had a transient bar during its evolution, but does 
	not have a bar at $z$ = 0. The~\citet{Minchev2013} model, and by extension 
	the~\citet{Minchev2014} and~\citet{Minchev2017} models as well, selected a 
	hydrodynamical simulation specifically so that it would have a bar at 
	$z$ = 0. This could mean that the dynamical history of our models Galaxies 
	do not reflect that of the~\citet{Minchev2013} model, and perhaps the 
	Milky Way itself. A detailed investigation on the impact of bar evolution 
	on stellar migration and thus chemical evolution is outside the scope of 
	this paper, though can be conducted in principle by simply swapping the 
	\texttt{h277} data within~\texttt{VICE} for another simulation, then 
	rerunning our numerical models and comparing the results.

@@

\subsection{Radial Migration} 
\label{sec:methods:migration} 
\begin{itemize} 
	\item To simulate our models, we develop and make use of \texttt{VICE}'s 
	\texttt{milkyway} object, an extension of a more general object named 
	\texttt{multizone}. The \texttt{multizone} object is at its core an array 
	of \texttt{singlezone} objects, which are designed to handle 
	simulations of one-zone models and were the focus of 
	\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
	\texttt{multizone} object then affords the user the ability to move 
	gas between zones with any given time dependence, and to assign all 
	stellar populations any given zone at any given time following their 
	birth, effectively allowing arbitrarily complex zone and migration 
	schema. The \texttt{milkyway} object is a user-friendly extension of this 
	which enforces a zone configuration in which the Galaxy is modeled as a 
	series of concentric annuli of uniform width~$\Delta R_\text{gal}$. As 
	defaults, it adopts the stellar migration model described in this section 
	and our star formation law described in~\S~\ref{sec:methods:sfe}.

@@

	\item In modeling the Milky Way as a series of concentric annuli,
	~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations to 
	be born at the centres of each annulus. For a stellar population born at a 
	time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for 
	star particles from~\texttt{h277} that formed at~$T \pm$ 250 Myr and 
	$R_\text{gal} \pm$ 250 pc. It then randomly selects a star particle from 
	this subsample with no bias to act as an~\textit{analog}. This stellar 
	population then assumes the change in orbital radius~$\Delta R_\text{gal}$ 
	of its analog at face value, and moves from its birth radius to the implied 
	final radius at $T$ = 12.2 Gyr with some time dependence. If no candidate 
	analogs are found,~\texttt{VICE} widens the search to~$T \pm$ 500 Myr and 
	$R_\text{gal} \pm$ 500 pc. While the maximum allowed difference in birth 
	times caps here at 500 Myr, we allow the difference in birth radii to 
	continue increasing by 250 pc until a candidate analog is found. 
	\begin{itemize} 
		\item In principle this allows stellar populations to be assigned 
		analogs with significantly different birth radii; however, this is only 
		an issue for small~$T$ and large~$R_\text{gal}$ where there are few 
		star particles from~\texttt{h277}, and where few stars form in nature 
		anyway due to the inside-out growth of Galaxies. Furthermore, due to 
		the similarity of the histograms in the top row of Fig. 
		\ref{fig:h277_decomposition}, we expect taking~$\Delta R_\text{gal}$ 
		from a star particle which formed at a similar time but different birth 
		radius in these instances to be accurate enough for our purposes.

		\item Each annulus in our models does not contain any vertical 
		information; that is, the displacements of stars from the disc midplane 
		$\left|z\right|$ does not enter into our models at all. After running 
		a~\texttt{VICE} simulation, each stellar population is simply assumed 
		to be located at the present-day~$z_\text{final}$ of its assigned 
		analog. In effect, this retains the assumption that the gas-phase 
		abundances are verticaly and azimuthally well-mixed, and that changes 
		in the gas composition at a given time happen only in the radial 
		direction.

		\item When a star particle is assigned as an analog to a stellar 
		population in our simulations, it is~\textit{not} thrown out of the 
		sample of candidate analogs, in theory allowing a star particle to act 
		as an analog for multiple stellar populations. This is a difference 
		between the~\citet{Minchev2013} model and ours. Where we assign star 
		particles to stellar populations for which~\texttt{VICE} then 
		calculates a stellar mass and composition based on an assumed star 
		formation history, the~\citet{Minchev2013} model assigns compositions 
		to star particles. 
	\end{itemize}

% fig 2 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time 
for two stellar populations under our migration schema: diffusion (crimson, 
solid), linear (lime, dot-dashed), post-process (black, dotted), and 
sudden (blue, dashed). Here the initial and final radii and birth times are 
chosen at random for illustrative purposes. With the initial and final 
Galactocentric radii of a stellar population, its birth time, and one of these 
assumptions about the time-dependence of migration, the Galactocentric radius 
at all times is known. } 
\label{fig:migration_schema} 
\end{figure}

	\item Our migration models 
	\begin{itemize} 
		\item With our data from the~\texttt{h277} simulation 
		providing a stellar population born at some radius~$R_\text{gal}$ and 
		time~$T$ with the required~$\Delta R_\text{gal}$, we construct the 
		following four models describing the time-dependence with which a 
		stellar population moves to its final radius.

		\item All models here neglect radial gas flows, this paper instead 
		focusing on these simple models describing how orbital radii change 
		with time. Investigation of our models with radial gas flows would be 
		an interesting extension to this paper.

@@

		\item \textbf{Diffusion}: A case in which stars migrate in a 
		continuous, time-dependent manner. If stars move to their final 
		radii via a random walk, then the mean displacement of stars that 
		migrate similar distances would scale with~$\sqrt{\text{age}}$. This 
		is shown in the red solid line in Fig.~\ref{fig:migration_schema}. 
		This is our fiducial migration model; we present results using this 
		model except where otherwise noted. It is so named because it 
		corresponds to a scenario in which the random walk carries out the 
		diffusion of angular momentum. This is qualitatively similar to 
		\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
		with a~$\sqrt{\tau}$ dependence.

@@

	\item We have a sample of 3,000,556 candidate analog star particles from 
	\texttt{h277}, only~$\sim$57\% of which are disc stars. Since we're 
	modeling the thin and thick disc populations here,~$\sim$1.71 million is a 
	much better estimate of the number of analogs that we can realistically 
	sample from. We take~$\Delta R_\text{gal}$ = 100 pc as the width of each 
	annulus from~$R_\text{gal}$ = 0 to 20 kpc and a timestep size of 
	$\Delta T$ = 10 Myr from $T$ = 0 to 12.2 Gyr (see discussion in~\S 
	\ref{sec:methods:h277} for our choice of time-interval). With the resulting 
	200 zones and 1,221 timesteps, we let~\texttt{VICE} from~$n$ = 9 stellar 
	populations per zone per timestep, resulting in 2,197,800 total stellar 
	populations with predicted masses and abundances. While this is more than 
	the number of disc particles in our sample of candidate analogs, we force 
	the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while 
	these stellar populations exist within~\texttt{VICE} and are a part of the 
	computational overhead, they have zero mass and thus do not contribute to 
	the chemical evolution. This results in 1,692,306 stellar populations 
	with~\textit{non-zero} masses and abundances predicted by~\texttt{VICE}, 
	reasonably within the limit of what we can sample. These simulations run in 
	$\sim$6 hours and take up~$\sim$235 MB of disc space per output, including 
	the extra data that we record for each stellar population's analog star 
	particle.
